---
title: "Weight Prediction"
author: "Krishna B. Thapa Magar"
date: "5/7/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

- I teach in Eastern New Mexico University. I asked my "Introductory Statistics" students to perform statistical finding on height and weight of males and females of our campus. They collected some sample to perform their work.
- I thought of using their dataset (with their permission) to make a linear prediction model on weight given their height.
- I decided to build two linear models: the first model using 43 female dataset to predict the weight of a female, and the second model using all 120 dataset to predict the weight of a person. 



## The dataset and two models

- The sample has height and weight of 77 female and 43 male.

```{r, comment=""}
data_fm<-read.csv("enmu_fm.csv")
data_f<-read.csv("enmu_f.csv")
summary(data_fm)
modelF<-lm(Weight~Height, data = data_f)
modelFm<-lm(Weight~Height, data = data_fm)
paste0("weight_F=", round(coef(modelF)[1],2) , "+" , round(coef(modelFm)[2],2) , "*" , "height_F")
paste0("weight=", round(coef(modelFm)[1],2) , "+" , round(coef(modelFm)[2],2) , "*" , "height")
```

## Scatterplot and linear model for Female weight

```{r}
plot(data_f$Height, data_f$Weight, xlab = "Height of Female (in inches)", 
         ylab = "Weight of Female (in lbs)", bty="n", pch=16,
         xlim = c(56,77), ylim = c(95, 285))
      abline(modelF, col="red", lwd=2)
```

## Scatterplot and linear model for a person's weight

```{r}
plot(data_fm$Height, data_fm$Weight, xlab = "Height of a person (in inches)", 
         ylab = "Weight of a person (in lbs)", bty="n", pch=16,
         xlim = c(56,77), ylim = c(95, 285))
      abline(modelFm, col="blue", lwd=2)
```

